Title Goes Here

### 2017-09-20 analysis/paper/saa2018_general_sessions_posters_hclust.Rmd
thinking about scheduling

```{r}
# Make clustering with `sc_clustering`
library(scclust)
my_dist <- distances(m)
my_clustering <- sc_clustering(my_dist, 3)

# Refine clustering with `hierarchical_clustering`
my_refined_clustering <- hierarchical_clustering(my_dist,
                                                 size_constraint = 4,
                                                 existing_clustering = my_clustering)

cuts <- my_refined_clustering 
```

```{r}
hc <- groups

@@

cuts <- hc$height + 1e-9

min_size <- 10
smallest <- 4
i <- 0

while(smallest < min_size & i <= length(cuts)){
  h_i <- cuts[i <- i+1]
  if(i > length(cuts)){
    warning("Couldn't find a cluster big enough.")
  }
  else  smallest <- 
           Reduce(min, 
                  lapply(X = unnest(cut(as.dendrogram(hc), h=h_i)$lower), 
                         FUN = attr, which = "members") ) # from lukeA's comment
}
h_i

cut(as.dendrogram(hc), h=h_i/2)
```

@@

```{r}
# histogram
freqs_per_cluster <- 
cuts %>%
  data_frame(cuts = .,
             freq = names(.)) %>% 
  group_by(cuts) %>% 
  tally()

>>>>

```{r}
library(dynamicTreeCut)
maxCoreScatter <- 0.99
minGap <- (1 - maxCoreScatter) * 0.01
dynamicCut <- cutreeDynamic(groups, 
                           minClusterSize=4, 
                           method="hybrid", 
                           distM=as.matrix(dist(m, method="euclidean")), 
                           deepSplit=4, 
                           maxCoreScatter=maxCoreScatter, 
                           maxAbsCoreScatter=NULL, 
                           minAbsGap=NULL)

hist(table(dynamicCut))

xfreqs_per_cluster <- 
dynamicCut %>%
  data_frame(dynamicCut = .,
             freq = names(.)) %>% 
  group_by(dynamicCut) %>% 
  tally(sort=TRUE)

hist(xfreqs_per_cluster$n)

library(dendextend)
hc <- groups
dend <- as.dendrogram(hc)
heights_per_k.dendrogram(dend)

@@

hc <- groups
cuts2 <- hc$height + 1e-9
# my experiment
for(i in seq_along(cuts2)){
  n <- attr(cut(as.dendrogram(groups), h=3)$lower[[i]], "members")
  print(n)
}

my_list <- cut(as.dendrogram(groups), h=3)
map(my_list, unnest(.x)$lower)

map(cut(as.dendrogram(groups), h=3), ~attr(.x$lower, "members"))

xcuts <- cutree(groups, k)

xfreqs_per_cluster <- 
xcuts %>%
  data_frame(cuts = .,
             freq = names(.)) %>% 
  group_by(cuts) %>% 
  tally(sort=TRUE)

xmax <- max(xfreqs_per_cluster$n)
xmin <- min(xfreqs_per_cluster$n)

max_size <- 16
min_size <- 4
n <- 0

while(xmax <= max_size &  xmin >= min_size & n <= length(xcuts)){
  n <-  n + 1
  ycuts <- cutree(groups, n)

xfreqs_per_cluster <- 
xcuts %>%
  data_frame(cuts = .,
             freq = names(.)) %>% 
  group_by(cuts) %>% 
  tally(sort=TRUE)

xmax <- max(xfreqs_per_cluster$n)
xmin <- min(xfreqs_per_cluster$n)

  xcuts <- cutree(groups, n)

}

```{r}

hc <- groups

hc$size

cuts2 <- hc$height + 1e-9

biggest <- 50
smallest <- 0

max_size <- 16
min_size <- 4

i <- 0

while(smallest < min_size & 
      biggest > max_size &
      i <= length(cuts2)){
  h_i <- cuts2[i <- i+1]
  if(i > length(cuts2)){
    warning("Couldn't find a cluster big enough.")
  }
  else  smallest <- 
           Reduce(min, 
                  lapply(X = unnest(cut(as.dendrogram(hc), h=h_i)$lower), 
                         FUN = attr, which = "members") ) # from lukeA's comment

  biggest <- 
           Reduce(max, 
                  lapply(X = unnest(cut(as.dendrogram(hc), h=h_i)$upper), 
                         FUN = attr, which = "members") ) # from lukeA's comment

  print(paste0("biggest: ", biggest, ", smallest: ", smallest, " i: ", i, " h_i: ", h_i))
}
h_i

cut(as.dendrogram(hc), h=h_i)
```

@@

```{r}
# histogram
freqs_per_cluster <- 
cuts %>%
  data_frame(cuts = .,
             freq = names(.)) %>% 
  group_by(cuts) %>% 
  tally(sort=TRUE)
